Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-12 TEBenchmarkPaper/article.tex
Add speedup table

% Derived from the template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{hhline}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{arrows, calc, decorations.pathreplacing, positioning,
  shapes.geometric}
% etc.

@@

For each sample size (``benchmark'') the Speedup-Test protocol compares the
distributions of each tool's times using a Kolmogorov-Smirnov test. If these are
significantly different (with $\alpha < 0.05$), then the signed-rank test is
only performed if more than 30 samples are available. This was the case for all
sample sizes except for 1 and 2 (due to the removed duplicates), and hence those
two speedups were not deemed statistically significant. For all other sample
sizes QuickSpec was found to be faster, with 95\% confidence. The speedup for
each size is given in table~\ref{FIXME}. The 95\% confidence interval for the
proportion of sample sizes where QuickSpec's median running time is faster than
IsaCoSy's is 66.9\% to 98.2\%.

>>>>

% Derived from the template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{csvsimple}
\usepackage{hhline}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{arrows, calc, decorations.pathreplacing, positioning,
  shapes.geometric}
% etc.

@@

For each sample size (``benchmark'') the Speedup-Test protocol compares the
distributions of each tool's times using a Kolmogorov-Smirnov test. If these are
significantly different (with $\alpha < 0.05$), then the signed-rank test is
only performed if more than 30 samples are available. This was the case for all
sample sizes except for 1 and 2 (due to the removed duplicates), and hence those
two speedups were not deemed statistically significant. For all other sample
sizes QuickSpec was found to be significantly faster with $\alpha = 0.05$,
giving a 95\% confidence interval for the proportion of (median) speedups to be
$[0.669;0.982]$. The magnitude of each speedup is is given in
table~\ref{table:speedups}.

\begin{table}
  \begin{tabular}{ |r|l| }
    \hline
    \bfseries Sample Size & \bfseries Speedup
    \csvreader[]{speedups.csv}{}
    {\\\hline\csvcoli&\csvcolii} \\
    \hline
  \end{tabular}
  \caption{Speedup when using QuickSpec compared to IsaCoSy for each sample
    size. Those which aren't statistically significant with 95\% confidence are
    marked as ``-''. These are conservative estimates, since the difference is
    bounded by the timeout.}
  \label{table:speedups}
\end{table}
